Details of specific functions

### 2019-09-09 inst/gitbook/03_specific-tutorials.Rmd
added examples for dispRity utilities matrix.dispRity

>>>>

If you have subsets in your `dispRity` object, you can also use the `matrix.dispRity` (see [utilities](#utilities)) and `colMeans` to get the centre of a specific subgroup.
For example

```{r, warning = FALSE}
## Create a custom subsets object
dummy_groups <- custom.subsets(dummy_space, group = list("group1" = 1:5, "group2" = 6:10))
summary(dispRity(dummy_groups, metric = centroids,
                 centroid = colMeans(matrix.dispRity(dummy_groups, "group1"))))
```
